### 2010-06-29 pkg/paper/Draft/draft-Z-W.tex
some papgers and comments
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/glogis@24 b679b2f7-6539-45d0-a605-5ddcb976cde9

\subsection{Belgium}
%% http://www.indexmundi.com/belgium/inflation_rate_%28consumer_prices%29.html
There was a  very sharp fall in yearly inflation in this time (from 2\% in December 1999 to 0.2\% in January 2000). Volatility  a very clear increase in volatility; from 1999 to 2000 we had a 137\% increase in the yearly inflation rate. Economic reason?

@@

\subsection{Ireland}
In recession since second quarter of 2008. The European country most severely hit by 
% (http://en.wikipedia.org/wiki/Economy_of_the_Republic_of_Ireland)

>>>>

\subsection{Belgium}
%% http://www.indexmundi.com/belgium/inflation_rate_%28consumer_prices%29.html
% Country Report Belgium  bei ebscohost in TX all text
There was a  very sharp fall in yearly inflation in this time (from 2\% in December 1999 to 0.2\% in January 2000). Volatility  a very clear increase in volatility; from 1999 to 2000 we had a 137\% increase in the yearly inflation rate. Economic reason: belgish franc was pegged to German Mark (since 1990). Possibly: Domestic inflation was mainly driven by the surge in world oil prices, with the result that energy prices in Belgium were around 25 \% higher in the first quarter of this year than in the year-earlier period. Also a general upward trend in prices.
% source: Belgium_3206697
tax reductions in personal income tax
% source: Belgium_4611003
inflation turns out to be more volatile in small, open economies such as Belgium (might be the case in some countries, but not in all of them). some explanations happen to be: a) a more volatile currency risk premium (which cannot be the case in Belgium, since it happend after 1.1999 and the currency was pegged thereafter, and even before pegged to Germany); b) degree of exchange--rate--passthrough to inflation (not possible as well) and c) size of monetary policy shocks (if there were any, should have to be observed in ALL EMU countries, since monetary policy equal). another possible explanation are productivity shocks which boost inflation rate volatility (but this for more than 10 years????)

[some connection with interest rate? maybe not the same until 1.2002 ?]
[volatility of inflation decreases the rate of growth]
%(growth_rate_vol_inflation)

@@

\subsection{Ireland}
In recession since second quarter of 2008. The European country most severely hit by the recession
% (http://en.wikipedia.org/wiki/Economy_of_the_Republic_of_Ireland)
